Modeling Interventions

### 2021-03-19 paper/paper.Rmd
edits

keywords          : "early language learning; language acquisition; vocabulary development"  
wordcount         : "2896"

@@

Reasoning from first principles, you cannot learn the word "table" if you do not hear it: input must predict learning. 
Yet correlational studies do not assess this relation fully, and instead assess whether variation in input relates to variation in learning. 
Thus, a second line of work focuses on differences between words, not children. 
These studies use regression models to predict which words are easier or more difficult, averaging across children [e.g., @goodman2008does; @braginsky2019]. 
They typically show a strong association between word frequency and the age at which children acquire particular words on average, especially for object labels. 
This general finding provides convergent support for accumulator models, absent the confound of differences between individuals.
In sum, accumulator models provide the conceptual underpinning of the relationships between input (freuqency for words, quantity for children) and learning.

@@

The core of the view that we are describing is that language learning is a process of accumulation. 
Individual experiences with words lead to their eventual acquisition. 
The more of these experiences a child receives, the faster their vocabulary grows. 
However, both children and words vary: children may learn faster or slower, and words can be more or less difficult to learn. 
Combining these ideas, the basic hypothesis is that a child’s vocabulary at a particular time should be predicted by their cumulative language exposure and learning rate, combined with the breadth of the sample of words to which have been exposed and those words' individual difficulties.

@@

We also included the frequency of each word as the key parameter controlling its accumulation, treating frequency as an item-level covariate of difficulty.
We do not have access to word frequencies in individual children's environments, however. 
Instead, we estimated average word frequencies by using the American English corpora in CHILDES [@macwhinney2000childes], following previous work [@goodman2008does;@braginsky2019].
<!-- IS THIS ^^ CORRECT? ALL AMERICAN ENGLISH? WHAT AGE CUTOFF? CHILDES-DB? -->
We estiamted that  an average child receives 1,200 words/hour, 12 hours/day, for a total of 438,300 tokens/month, of which 285,200 tokens (65.1%) are tokens of words appearing on the CDI. 
<!-- HOW WAS THIS ^^ COMPUTED! NEED AN APPENDIX OR NOTES IN THE REPO OR SOMETHING -->
We then included frequency estimates for each word of the tokens per month heard by a typical child (range: 0.2 - 19,286 tokens).

@@

**Leveraged learning and the role of processing**. 
As our results above show, older children accumulate language from their input faster than younger children.
Why?
Are older children simply better at remembering words, leading to "bigger drops" in the bucket for older children? 
Or children *leverage* their knowledge of language to learn faster [@mitchell2009]? 
They could do this by reasoning about new words by exclusion [@markman1988children]. 
Or their increasing fluency with the words they know could help them learn new words. A surprising proportion of variance in the rate of young children’s vocabulary growth is accounted for by the speed with which they process familiar words [e.g., @marchman2016early].
These theories predictions about which words should faciliate which others predictions that could be tested using the models we describe.

>>>>

keywords          : "early language learning; language acquisition; vocabulary development"  
wordcount         : "2921"

@@

Reasoning from first principles, you cannot learn the word "table" if you do not hear it: input must predict learning of individual words. 
Yet correlational studies do not assess this word-level relation fully, and instead assess whether variation in input relates to variation in learning across children. 
However, a second line of work focuses on differences between words, not children. 
These studies use regression models to predict which words are easier or more difficult, averaging across children [e.g., @goodman2008does; @braginsky2019]. 
They typically show a strong association between word frequency and the age at which children acquire particular words on average, especially for object labels. 
This general finding provides convergent support for accumulator models, absent the confound of differences between individuals.
In sum, accumulator models provide the conceptual underpinning of the relationships between input (frequency for words, quantity for children) and learning.

@@

The core of the view that we are describing is that language learning is a process of accumulation. 
Individual experiences with words lead to their eventual acquisition. 
The more of these experiences a child receives, the faster their vocabulary grows. 
However, both children and words vary: children may learn faster or slower, and words can be more or less difficult to learn. 
Combining these ideas, the basic hypothesis is that a child’s vocabulary at a particular time should be predicted by their cumulative language exposure and learning rate, combined with the breadth of the sample of words to which they have been exposed and those words' individual difficulties.

@@

We also included the frequency of each word as the key parameter controlling its accumulation, treating frequency as an item-level covariate of difficulty.
We do not have access to word frequencies in individual children's environments, however. 
Instead, we estimated average word frequencies using the American English corpora in CHILDES [@macwhinney2000childes] retrieved from childes-db [@sanchez2019childes], following previous work [@goodman2008does;@braginsky2019].
<!-- need to specify age cut-off? ToDo GK - believe it was all data -->
We estimated that an average child receives 1,200 words/hour, 12 hours/day, for a total of 438,300 tokens/month, of which 285,200 tokens (65.1%) are tokens of words appearing on the CDI (see Appendix). 
<!-- HOW WAS THIS ^^ COMPUTED! NEED AN APPENDIX OR NOTES IN THE REPO OR SOMETHING -->
We then included frequency estimates for each word of the tokens per month heard by a typical child (range: 0.2 - 19,286 tokens).

@@

**Leveraged learning and the role of processing**. 
As our results above show, older children accumulate language from their input faster than younger children.
Why?
Are older children simply better at remembering words, leading to "bigger drops" in their buckets? 
Or do older children *leverage* their knowledge of language to learn faster than younger children [@mitchell2009]? 
They could do this by reasoning about new words by exclusion [@markman1988children]. 
Or could their increasing fluency with the words they know help them learn new words? 
A surprising proportion of variance in the rate of young children’s vocabulary growth is accounted for by the speed with which they process familiar words [e.g., @marchman2016early].
These theoretical proposals about which words should facilitate the learning of other words yield predictions that could be tested using the models we describe.
